### 2018-08-08 paper/approach.tex

Further, \ac{SPOR} protocol (\cref{design}) adds node selection on top of \Sphinxes.
The \ac{SPOR} protocol (Figure~\ref{fig:outline} \ding{203})  assumes a source of random nodes, \eg through 
\ac{RPS}~\cite[\eg][]{BrahmsRPS} or \iac{DHT} based 
scheme~\cite[\eg][]{Octopus}.
Each node must be associated with a public key and some availability 
prediction.
\Ac{SPOR} selects nodes for a route uniformly randomly and uses the 
availability to maximize the availability of the entire route, \ie across 
layers.
As \ac{SPOR} assumes this source of random nodes, the network view (routing 
information) of each node depends on this source of random nodes, as does the 
fact of how decentralized the scheme becomes and whether the network toppology 
is fully, mostly or partly connected (network structure).
As \ac{SPOR} is designed, it selects nodes uniformly among all the nodes 
(communication model, node selection) that the source of random nodes provides.
Thus, ultimately, these also depends on the source of random nodes.

>>>>

Further, the \ac{SPOR} protocol (\cref{design}) adds node selection on top of \Sphinxes.
The \ac{SPOR} protocol (Figure~\ref{fig:outline} \ding{203})  assumes a source of random nodes, \eg through 
\ac{RPS}~\cite[\eg][]{BrahmsRPS} or \iac{DHT} based 
scheme~\cite[\eg][]{Octopus}.
Each node must be associated with a public key and some availability 
prediction.
\Ac{SPOR} selects nodes for a route uniformly randomly and uses the 
availability to maximize the availability of the entire route, \ie across 
layers.
\commentFT{What follows seems quite convoluted, with a lot of repetition. Would be nice to revise.} As \ac{SPOR} assumes this source of random nodes, the network view (routing 
information) of each node depends on this source of random nodes, as does the 
fact of how decentralized the scheme becomes and whether the network toppology 
is fully, mostly or partly connected (network structure).
As \ac{SPOR} is designed, it selects nodes uniformly among all the nodes 
(communication model, node selection) that the source of random nodes provides.
Thus, ultimately, these also depends on the source of random nodes.

### 2018-08-08 paper/intro.tex

The remainder of this paper is organized as follows. Section~\ref{system-model} presents the
system and adversary models as well as the desired security and privacy properties of \name. Section~\ref{design}
introduces the design of our proposed solution. In
Sections~\ref{security-discussion} and \ref{Performance},
respectively, we evaluate the security and performance of our
approach. We set \name into context with related work in
Section~\ref{RelatedWork} and conclude with Section~\ref{conclusion}.

>>>>

The remainder of this paper is organized as follows. Section~\ref{system-model} presents the
system and adversary models as well as the desired security and
privacy properties of \name. Section~\ref{approach} describes the
overall approach. In Section~\ref{Sphinxes}, we introduce \sphinxes. 
Then, in Section~\ref{design}, we introduce the different building
blocks of \name. In sections~\ref{security-discussion} and \ref{Performance},
respectively, we evaluate the security and performance of our
approach. We set \name into context with related work in
Section~\ref{RelatedWork}, and finally conclude with Section~\ref{conclusion}.

### 2018-08-08 paper/related.tex

The main concern arising from unreliable nodes, which is shared with traditional P2P file sharing, is \emph{churn}~\cite{dhtchurn} and its effect on availability. % - here in the narrow context of the set of user devices based on user behavior. 
Most P2P approaches have addressed churn in the past by combining in various ways \emph{data replication} (e.g. by storing the same file chunk on multiple nodes) and \emph{routing redundancy} (e.g. by maintaining multiple independent paths to the same node). Data replication does not work in our case as we prioritize privacy and independence from third-party storage. The probabilistic onion routing we propose can be interpreted as a form of routing redundancy, albeit one that is built from the ground up to ensure strong privacy guaranties.

>>>>

The main concern arising from unreliable nodes, which is shared with traditional P2P file sharing, is \emph{churn}~\cite{dhtchurn} and its effect on availability. % - here in the narrow context of the set of user devices based on user behavior. 
Most P2P approaches have addressed churn in the past by combining in various ways \emph{data replication} (e.g. by storing the same file chunk on multiple nodes) and \emph{routing redundancy} (e.g. by maintaining multiple independent paths to the same node). Data replication does not work in our case as we prioritize privacy and independence from third-party storage. The probabilistic onion routing we propose can be interpreted as a form of routing redundancy, albeit one that is built from the ground up to ensure strong privacy guarantees.

### 2018-08-08 paper/security-discussion.tex

With an inaccurate availability function, \(\avail\), this will not be a 
problem as there will be many others (as the system scales) that shares the 
same availability distribution.
With more accurate availability estimates we would have to employ techniques 
like \ac{DP} to ensure that Alice's availability distribution is not too 
unique.

@@

Stateless routing can result in re-ordered chunks or packets, and
chunks received on different devices of a user's \squad. From Sphinx,
we inherit unique IDs for each mix packet.
If we provide the mix packets as an ordered list when we communicate them 
out-of-band together with the metadata of the file and they are used in that 
same order, then we can use those IDs to re-order chunks if need be.
The \squad overlay handles inter-squad \commentDaniel{intra?} device 
coordination.
We ensure liveness by acknowledgments and timeouts (as detailed in 
\cref{sec:squad_overlay}), despite the possibility of \squad devices
going offline during transfer or other node or link failures.

>>>>

With an inaccurate availability function, \(\avail\), this will not be a 
problem as there will be many others (as the system scales) that share the 
same availability distribution.
With more accurate availability estimates we would have to employ techniques 
like \ac{DP} to ensure that Alice's availability distribution is not
(too close to)
unique.

@@

Stateless routing can result in re-ordered chunks or packets, and
chunks received on different devices of a user's \squad. From Sphinx,
we inherit unique IDs for each mix packet.
If we provide the mix packets as an ordered list when we communicate them 
out-of-band together with the metadata of the file and they are used in that 
same order, then we can use those IDs to re-order chunks if need be.
The \squad overlay handles intra-squad device 
coordination.
We ensure liveness by acknowledgments and timeouts (as detailed in 
\cref{sec:squad_overlay}), despite the possibility of \squad devices
going offline during transfer or other node or link failures.
